Interested in joining the team

### 2025-01-21 join.qmd
change text placement
change contact email

If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab [at] mcmaster [dot] ca.

@@

>>>>

@@

If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to cartem11 [at] mcmaster [dot] ca. Incomplete applications will not be reviewed.
